---
title: "Distributions"
output: html_notebook
---

## Bernoulli distribution

Binary outcomes - coins, biased coins, etc...

Mean = p
Var = p(1-p)

## Binomial 

N times Bernoulli - Sum of a Bernoulli

(n choose x) stuff

Suppose a friend has 8 children, 7 of which are girls. 
If each gender has an independent 0.5 probability for each birth, what's the probability of getting 7 or more girls out of 8 births?

```{r}
choose(8,7)*0.5^8 + choose(8,8)*0.5^8 #Proba of 7 + Proba of 8

pbinom(6, size = 8, prob = .5, lower.tail = F)
```

## Normal

X ~ N(m, sigma^2)

- the standard normal distribution - m = 0, std.dev = 1
- all not-standard calculations rever to a standard normal one.

For example, for standard normal 1.28 is 90th quantile. For non-standard, you need m + 1.28*st.d

| Here are two useful facts concerning normal distributions. If X is a normal random variable with mean mu and variance sigma^2, i.e., X ~
| N(mu,sigma^2),
| then the random variable Z defined as Z = (X -mu)/sigma is normally distributed with mean 0 and variance 1, i.e., Z ~ N(0, 1). (Z is standard
| normal.)
| The converse is also true. If Z is standard normal, i.e., Z ~ N(0,1), then the random variable X defined as X = mu + sigma*Z is normally
| distributed with mean mu and variance sigma^2, i.e., X ~ N(mu, sigma^2)

```{r}
qnorm(0.95) #95th percentile, for different normal mean = mu, sd = sd
#m + sd*1.645

#What is the probability that a N(m, sigma^2) RV is larger than x
#pnorm(x, mean = m, st.dev = sigma, lower.tail = F)

#Alternatively, convert (X - m)/st.dev

#m = 1020, st.dev = 50. Whats the proba of getting more than 1160 clicks.

(1160 - 1020)/50 #2.8 stdev from the mean, so expect below 1%
pnorm(1160, mean = 1020, sd = 50, lower.tail = F)
#Same as the below
1 - pnorm(1160, mean = 1020, sd = 50)

#Same as above, what x is 75% of days have fewer clicks 
#Intuition - 0.5 + 1sd should be around 0.84, so i'd expect around 1060 (1020 + a bit less than 50)
qnorm(0.75, mean = 1020, sd = 50)


```

## Poisson distribution

Model counts - can't go below zero
Model event-time or survival data
Model contingency tables (think hair color by race)
Approximating binomials when n is large and p is small - Think Air polutions, and respiratory 
Big city, small respiratory

Lambda = is the expected count per unit of time
t is the total monitor of time.

Mean = Var = Lambda - 

The number of people that show up at a bus stop is Poisson with a mean of 2.5 per hour.
If watching the bus stop for 4 hours, what is the probability that 3 or fewer people show up for the whole time?

```{r}
ppois(3, lambda = 2.5*4) #Note 2.5 times 4 hours
```

### Poisson approximation of the binomial.

We flip a coin with success proba of 0.01 500 times. What's the probability of 2 or fewer successes?
```{r}
pbinom(2, size = 500, prob = 0.01)
ppois(2, lambda = 500*0.01)

```

