---
title: "Robust Student's T Regression with BRMS - walkthrough on Solomon Kurz's post"
output: html_notebook
---

https://solomonkurz.netlify.app/post/2019-02-02-robust-linear-regression-with-student-s-t-distribution/

```{r}
library(tidyverse)

tibble(x = seq(from = -6, to = 6, by = .01)) %>% 
  expand(x, nu = c(1, 2.5, 5, 10, Inf)) %>% 
  mutate(density = dt(x = x, df = nu),
         nu      = factor(nu, levels = c("Inf", "10", "5", "2.5", "1"))) %>% 
  
  ggplot(aes(x = x, y = density, group = nu, color = nu)) +
  geom_line() +
  scale_color_viridis_d(expression(nu),
                        direction = 1, option = "C", end = .85) +
  scale_y_continuous(NULL, breaks = NULL) +
  coord_cartesian(xlim = c(-5, 5)) +
  xlab(NULL) +
  theme(panel.grid = element_blank()) +
  labs(title = "The bigger the n, the closer is Student's T to Gaussian")
```
So the difference is that a Student’s -distribution with a low  will have notably heavier tails than the conventional Gaussian distribution. It’s easiest to see the difference when  approaches 1. Even then, the difference can be subtle when looking at a plot. Another way is to compare how probable relatively extreme values are in a Student’s -distribution relative to the Gaussian. For the sake of demonstration, here we’ll compare Gauss with Student’s  with a  of 5. In the plot above, they are clearly different, but not shockingly so. However, that difference is very notable in the tails.
```{r}
# here we pic our nu
nu <- 5

tibble(z_score               = 0:-5,
       p_Gauss               = pnorm(z_score, mean = 0, sd = 1),
       p_Student_t           = pt(z_score, df = nu),
       `Student/Gauss ratio` = p_Student_t/p_Gauss) %>%
  mutate_if(is.double, round, digits = 5) %>% 
  knitr::kable()
```
## Simulation Time

Variance/covariance matrix.
```{r}
s <- matrix(c(1, .6, 
              .6, 1), 
             nrow = 2, ncol = 2)
print(s)
print('0.6 is the true relationship')

#means
m <- c(0, 0)

set.seed(3)

d <- MASS::mvrnorm(n = 100, mu = m, Sigma = s) %>%
  as_tibble() %>%
  rename(y = V1, x = V2)

d <-
  d %>%
  arrange(x)

print(head(d))

ggplot(d, aes(x, y)) + 
  geom_point()
```


```{r}
o <- d
o[c(1:2), 1] <- c(5, 4.5)

head(o)
ggplot(o, aes(x, y)) + 
  geom_point()
```
```{r}
ols0 <- lm(data = d, y ~ 1 + x)
ols1 <- lm(data = o, y ~ 1 + x)

library(broom)

tidy(ols0) %>% mutate_if(is.double, round, digits = 2)
tidy(ols1) %>% mutate_if(is.double, round, digits = 2)
```

```{r}
# the well-behaved data
p1 <-
  ggplot(data = d, aes(x = x, y = y)) +
  stat_smooth(method = "lm", color = "grey92", fill = "grey67", alpha = 1, fullrange = T) +
  geom_point(size = 1, alpha = 3/4) +
  scale_x_continuous(limits = c(-4, 4)) +
  coord_cartesian(xlim = c(-3, 3), 
                  ylim = c(-3, 5)) +
  labs(title = "No Outliers") +
  theme(panel.grid = element_blank())

# the data with two outliers
p2 <-
  ggplot(data = o, aes(x = x, y = y, color = y > 3)) +
  stat_smooth(method = "lm", color = "grey92", fill = "grey67", alpha = 1, fullrange = T) +
  geom_point(size = 1, alpha = 3/4) +
  scale_color_viridis_d(option = "A", end = 4/7) +
  scale_x_continuous(limits = c(-4, 4)) +
  coord_cartesian(xlim = c(-3, 3), 
                  ylim = c(-3, 5)) +
  labs(title = "Two Outliers") +
  theme(panel.grid = element_blank(),
        legend.position = "none")

# combine the ggplots with patchwork syntax
library(patchwork)

p1 + p2
```

```{r}
aug0 <- augment(ols0)
aug1 <- augment(ols1)

glimpse(aug1)
```

```{r}
bind_rows(
  aug0 %>% mutate(i = 1:n()),  # the well-behaved data
  aug1 %>% mutate(i = 1:n())   # the data with two outliers
) %>%
  mutate(fit = rep(c("fit b0", "fit b1"), each = n()/2)) %>%
  ggplot(aes(x = i, y = .cooksd)) +
  geom_hline(yintercept = .5, color = "white") +
  geom_point(alpha = .5) +
  geom_text(data = tibble(i = 46, 
                          .cooksd = .53,
                          fit = "fit b0"),
            label = "Fahrmeir et al said we might worry around here",
            color = "grey50") +
  coord_cartesian(ylim = c(0, .7)) +
  theme(panel.grid = element_blank(),
        axis.title.x = element_text(face = "italic", family = "Times")) +
    facet_wrap(~ fit)
```

```{r}
library(brms)
```

```{r}
b0 <- 
  brm(data = d, 
      family = gaussian,
      y ~ 1 + x,
      prior = c(prior(normal(0, 10), class = Intercept),
                prior(normal(0, 10), class = b),
                prior(cauchy(0, 1),  class = sigma)),
      seed = 1)
```

```{r}
posterior_summary(b0)[1:3, ] %>% round(digits = 2)
```

```{r}
b1 <- 
  brm(data = o, 
      family = gaussian,
      y ~ 1 + x,
      prior = c(prior(normal(0, 10), class = Intercept),
                prior(normal(0, 10), class = b),
                prior(cauchy(0, 1),  class = sigma)),
      seed = 1)

posterior_summary(b1)[1:3, ] %>% round(digits = 2)
```

```{r}
loo_b0 <- loo(b0)
loo_b1 <- loo(b1)

str(loo_b1)
```

```{r}
loo_b1$diagnostics$pareto_k %>% as_tibble()
```
```{r}
library(loo)

pareto_k_table(loo_b1)
```

```{r}
plot(loo_b1)
```

```{r}
b2 <- 
  brm(data = o, family = student,
      y ~ 1 + x,
      prior = c(prior(normal(0, 10), class = Intercept),
                prior(normal(0, 10), class = b),
                prior(gamma(2, 0.1), class = nu),
                prior(cauchy(0, 1),  class = sigma)),
      seed = 1)
```


```{r}
# data
tibble(x = seq(from = 0, to = 60, by = .1)) %>% 
  expand(x, nesting(alpha = c(2, 4), 
                    beta  = c(0.1, 1))) %>% 
  mutate(density = dgamma(x, alpha, beta),
         group   = rep(letters[1:2], times = n() / 2)) %>% 
  
  # plot
  ggplot(aes(x = x, ymin = 0, ymax = density, 
             group = group, fill = group)) +
  geom_ribbon(size = 0, alpha = 3/4) +
  scale_fill_viridis_d(option = "B", direction = -1, 
                       begin = 1/3, end = 2/3) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.05))) +
  scale_y_continuous(NULL, breaks = NULL) +
  coord_cartesian(xlim = c(0, 50)) +
  theme(panel.grid = element_blank(),
        legend.position = "none")
```
```{r}
b3 <- 
  update(b2,
         prior = c(prior(normal(0, 10), class = Intercept),
                   prior(normal(0, 10), class = b),
                   prior(gamma(4, 1),   class = nu),
                   prior(cauchy(0, 1),  class = sigma)),
         seed = 1)
```

