---
title: "Sliced 7 - D. Rob Walkthrough"
output: html_notebook
---

Data dictionary
The variables are pretty self-explanatory. Two exceptions:

'id': unique identifier for the customer
'attrition_flag': whether the customer is churned (0 = no; 1 = yes)
'customer_age': age of the customer
'gender': gender of the customer
'education_level': education level of the customer
'income_category': income range of the customer
'total_relationship_count': number of relationships
'months_inactive_12_mon': number of months the customer is inactive in the past 12 months
'credit_limit': the customer's credit limit
'total_revolving_bal': the customer's total revolving balance
'total_amt_chng_q4_q1': the amount the balance changed from Q4 to Q1
'total_trans_amt': the value of all the customer's transactions in the period
'total_trans_ct': the number of all of the customer's transactions
'total_ct_chng_q4_q1': the difference in number of the customer's transactions from Q4 to Q1
'avg_utilization_ratio': the customer's average utilization ratio during the period

```{r}
library(tidymodels)
library(tidyverse)
library(scales)
library(lubridate)
library(stacks)
theme_set(theme_light())

doParallel::registerDoParallel(cores = 4)
```

```{r}
dataset <- read_csv("data/sliced-s01e07/train.csv") %>% 
  mutate(churned = ifelse(attrition_flag == 1, "yes", "no")) %>% 
  select(-attrition_flag)
holdout <- read_csv("data/sliced-s01e07/test.csv")

set.seed(2021)
spl <- initial_split(dataset)
train <- training(spl)
test <- testing(spl)

train_5fold <- train %>% 
  vfold_cv(5)
```

```{r}
summarize_churn <- function(tbl){
  tbl %>% 
    summarize(
      n = n(),
      n_churned = sum(churned == 'yes'),
      pct_churned = n_churned/n,
      low = qbeta(.025, n_churned + .5, n - n_churned + .5),
      high = qbeta(.975, n_churned + .5, n - n_churned + .5)
    ) %>% 
    arrange(desc(n))
}

plot_categorical <- function(tbl, category, ...) {
  if (!is.factor(pull(tbl, {{category}}))) {
    tbl <- tbl %>% 
      mutate({{category}} := fct_reorder({{category}}, pct_churned))
  }
  tbl %>% 
    ggplot(aes(pct_churned, {{category}}, ...)) +
    geom_col(position = position_dodge()) +
    geom_errorbarh(position = position_dodge(width = 1), aes(xmin = low, xmax = high), height = .2) +
    scale_x_continuous(labels = percent) +
    labs(x = "% in category that churned")
}

train %>% 
  group_by(gender) %>% 
  summarize_churn() %>% 
  plot_categorical(gender)

train %>% 
  group_by(education_level) %>% 
  summarize_churn() %>% 
  plot_categorical(education_level)

train %>% 
  group_by(education_level, gender) %>% 
  summarize_churn() %>% 
  plot_categorical(education_level, fill = gender, group = gender)

train %>% 
  mutate(income_category = fct_reorder(income_category, parse_number(income_category)),
         income_category = fct_relevel(income_category, "Less than $40K")
         ) %>% 
  group_by(income_category, education_level) %>% 
  summarize_churn() +
  plot_categorical(income_category) +
  coord_flip()
 ```

