---
title: "Variability"
output: html_notebook
---

# Variability

## Variance

Handy:

Var(X) = E[X^2] - E[X]^2

Think of variance of the variance itself and its going slimmer and slimmer with sample size. 

Var(Xhat) = sigma^2/n - variance of the sample mean decreases to zero as the sample increases.
The above is the standard error of a mean - variability of mean. 


S - the standard deviation, talks about how variable the population is.
S/sqrt(n) - the standard error, talks about how variable averages of random samples of size n from the population are.

BOth of the above, of the mean - SD of the mean, SE of the mean

```{r}
nosim <- 1000
n <- 10

sd(apply(matrix(rnorm(nosim * n), nosim), 1, mean))

print(1/sqrt(10)) # normal distribution with S - 1
```

```{r}
nosim <- 1000
n <- 10

sd(apply(matrix(rpois(nosim * n, 4), nosim), 1, mean))

print(2/sqrt(n)) #pois
```

```{r}
nosim <- 1000
n <- 10

sd(apply(matrix(sample(0:1, nosim*n, replace = T), nosim),1 , mean))

print(1/(2*sqrt(n))) #Coin flips
```

```{r}
library(UsingR)
data(father.son)

x <- father.son$sheight
n <- length(x)

hist(x, prob = T)
lines(density(x))
```
```{r}
round(c(
  variance_sample = var(x), #estimates of the population, if random sample
  variance_averages_10_children_heights = var(x)/n, #variance of sample mean
  st_dev_sample = sd(x), #estimates of the population, if random sample
  st_dev_averages_10_children_heights = sd(x)/sqrt(n) #Standard Error 
),2)
```

